---
title: "Analyses on the classification of urbanized regions"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
library("randomForest")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
load_data()
knitr::opts_chunk$set(echo = TRUE)
```

This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency. All code <!--and data--> are available at <https://github.com/jakkermans/Open-Science-Introdcuction.git>.

This is an example of a non-essential citation [@@vanlissaWORCSWorkflowOpen2020]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

## Introduction

This project focused on the Sustainable Development Goals, which were created in 2015 by the United Nations. These goals serve the purpose of improving the world and should be achieved by 2030. Recently, the Global Data Lab (GDL) conducted household surveys in various subnational regions to collect data on several socioeconomic, health and demographic variables. The current dataset created by the GDL contains 126 indicators for 1337 subregions in 128 countries. A subset of the data will be used to answer the question 'How well can highly urbanized regions versus lowly urbanized regions be classified?'.

## Methods

How was the sample size determined, which data exclusions were used, all manipulations

## Participants

Who are the participants in the study

## Procedure


## Results

Classification through logistic regression and random forest yielded the following results:

```{r}
set.seed(123)
accuracy <- function(predictions, answers){sum((predictions==answers)/length(answers))} #function to calculate the accuracy of a classifier
ntrain <- round(nrow(scaled_urban_data)*3/4) #determine how many observations are needed for the training set
train <- sample(1:nrow(scaled_urban_data), ntrain) #sample the observations to be included in the training set

#Logistic regression results
urban_model <- glm(urban ~ ., data = scaled_urban_data[train,], family = "binomial")
urban_preds <- round(predict(urban_model, newdata = scaled_urban_data[-train,], type = "response"))
urban_preds <- ifelse(urban_preds==1,"low", "high")
accuracy(urban_preds, scaled_urban_data[-train,3])
table(urban_preds, scaled_urban_data[-train,3])


#Random Forest
urban_forest <- randomForest(urban ~ ., data = scaled_urban_data[train,], importance = TRUE, ntree = 2000, mtry = 5)
urban_forest_preds <- predict(urban_forest, newdata = scaled_urban_data[-train,])
accuracy(urban_forest_preds, scaled_urban_data[-train,3])
table(urban_forest_preds, scaled_urban_data[-train,3])
```

## Discussion

Here comes a conclusion
